---
title: "R Notebook"
output: word_document
---

4.2310 gonorrhea cases/10,000 people in an urban county 50/100,000 statewide. Probability of a case basedon the statewide data = 50/10,000 = 0.0005. Using the binomial distribution: Pr(X >= 10) when X ~binomial(n = 10000, p = 0.0005)

```{r}
1- pbinom(9, size = 10000, prob = 0.0005)
```

Using the Poisson distribution:μ= np = 100000.0005 = 5 Pr(X >= 10) when X ~ Poisson(μ= 5)

```{r}
ppois(9, lambda=5, lower.tail = FALSE)
```



4.31Given that 50% of hypertensives do not know they have high blood pressure so 50% do know that theyhave high blood pressure. Using the binomial distribution: Pr(X >= 7) when X ~ binomial(n = 10, p = 0.50))

```{r}
1- pbinom(6, size = 10, prob = 0.5)
```


Given that 40% of light users are HIV positive and 55% of heavy users are HIV positive. Using thebinomial distribution: Pr(X = 3) when X ~ binomial(n = 5, p = 0.40)

```{r}
dbinom(3, size = 5, prob = 0.4)

```


4.55Using the binomial distribution: Pr(X >= 3) when X ~ binomial(n = 5, p = 0.40)

```{r}
1- pbinom(2, size = 5, prob = 0.4)
```


4.86Want to computeμ= the average number of teeth lost per year.
```{r}
0*(35763/38905)+1*(1978/38905)+2*(591/38905)+3*(151/38905)+4*(163/38905)+7*(106/38905)+12*(

```

4.89Want to compute the probability of at least one admission on a weekday. Using the Poisson distribution:Pr(X >= 1) when X ~ Poisson(μ= 2)

```{r}
ppois(0, lambda=2, lower.tail = FALSE)
```

4.90Want to compute the probability of at least one admission on a weekend day. Using the Poissondistribution: Pr(X > 1) when X ~ Poisson(μ= 1)

```{r}
ppois(0, lambda=1, lower.tail = FALSE)
```






