---
title: "R Notebook"
output: word_document
---
11.13 Generate scatterplot with fitted regression line.

```{r}
# Enter data
age <-seq(1:17)
sbp <-c(99, 102, 105, 107, 108, 110, 111, 112, 114, 115, 117, 120, 122, 125, 127, 130, 132)
df <-data.frame(age, sbp)
model <-lm(df$sbp~df$age)
with(df,plot(age, sbp, main = "90th percentile SBP versus Age for boys ages 1-19"))
abline(model)
```

```{r}
summary(model)

```


11.14CI:
```{r}
confint(model, level = .95)

```


11.15Using the equation above:

```{r}
E_sbp <- 97.78676+1.919118*13
E_sbp
attach(df)
newdata <-data.frame(age=13)
predict(model, newdata, se.fit = TRUE, interval="confidence")
```


11.18 From the plot above the regression line underestimates values for the younger and older ages andoverestimates values in the middle age range. Generate the residuals plot versus age.

```{r}
library(olsrr)
ols_plot_resid_fit(model)
```


11.46 Fit the linear regression model for full-scale IQ (IQF) versus lead group with adjustment for age andgender:

```{r}
model1 <-lm(lead$iqf~lead$Group+lead$ageyrs+lead$sex)
summary(model1)

```


```{r}
ols_plot_resid_qq(model1)
```



```{r}
ols_plot_resid_hist(model1)

```


```{r}
ols_plot_diagnostics(model1)
```


Correlation test: 

```{r}
load("C:/Users/Joel Parker/Desktop/Bios 536A/BIOS576B/R/VALID.DAT.rdata")
cor.test(valid$alco_dr, valid$alco_ffq, method =c("spearman"))

```





