---
title: "R Notebook"
output: word_document
---

8.3 Two sample t test. Since the sample sizes are not equal we will assume unequal variances.
```{r, warning=FALSE}
library(PASWR)
tsum.test(mean.x = 6.56, s.x = 0.64, n.x = 25,mean.y = 6.8, s.y = 0.76 , n.y = 40,alternative = "two.sided", mu = 0,var.equal = FALSE, conf.level = 0.95)
```


library(MESS)# Will need the MESS package for the power function:
```{r}
library(MESS)
power_t_test(n=NULL, power=0.8, sd = 0.64, ratio=1, sd.ratio=0.76/0.64, delta=(6.8-6.56))

```



8.15 Two sample t test. Since the sample sizes are not equal we will assume unequal variances\

```{r}
t.test(wbc~Bact_cul, data = hospital, alternative = "two.sided", var.equal = FALSE)

```


8.19 Paired t test for Methazolamide and topical glaucoma medications.

```{r}
tsum.test(mean.x =-1.6, s.x = 1.5, n.x = 10,alternative = "two.sided", mu = 0,var.equal = FALSE, conf.level = 0.95)

```


8.22 Two sample t test. Since the sample sizes are not equal we will assume unequal variance.

```{r}
tsum.test(mean.x =-1.6, s.x = 1.5, n.x = 10,mean.y =-0.7, s.y = 2.1 , n.y = 30,alternative = "two.sided", mu = 0,var.equal = FALSE, conf.level = 0.95)
```

